%-------------------------
% Resume in LaTeX
% Author : Sri Villiam Sai
% License : MIT
%------------------------


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Sri Villiam Sai A} \\ \vspace{8pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 7339312067 ~ \href{mailto:srivilliamsai@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{srivilliamsai@gmail.com}} ~ 
    \href{https://linkedin.com/in/srivilliamsai}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/srivilliamsai}} ~
    \href{https://github.com/srivilliamsai}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/srivilliamsai}}
    \vspace{0pt}
\end{center}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, Swift, JavaScript, TypeScript, SQL} \\ \vspace{3pt}
     \textbf{Frameworks}{: Spring Boot, Spring MVC, Spring Cloud, Spring Security, JPA/Hibernate, React.js, Tailwind CSS} \\ \vspace{3pt}
     \textbf{Technologies \& Tools}{: Flutter, Bootstrap, Git, GitHub, Postman, Figma, Eclipse, VS Code, Xcode, REST APIs, Docker, MySQL, Firebase, Redis, Kubernetes, Kafka} \\ \vspace{3pt}
     \textbf{Soft Skills}{: Leadership, Problem-Solving, Innovation \& Creativity, Agile Practices (Scrum), Teamwork}
    }}
 \end{itemize}
 \vspace{-16pt}

 %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SRM Valliammai Engineering College}{Oct 2020 -- Apr 2024}
      {B.Tech. in Information Technology (CGPA: 7.80/10)}{Chennai, India}
  \resumeSubHeadingListEnd
\vspace{-8pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Infosys Springboard}{Nov 2025 -- Jan 2026}
      {Java Full Stack}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Built a full-stack personal carbon footprint tracker using React.js and Spring Boot, integrating external REST APIs to calculate carbon data while developing interactive user features like leaderboards and an eco-marketplace.}
        \resumeItem{Optimized API response times with Redis caching, secured user data using JWT authentication and Role-Based Access Control (RBAC), and successfully deployed the application using Docker and Kubernetes.}
        \resumeItem{Java, Spring Boot, React.js, Tailwind CSS, MySQL, Redis, Kubernetes, Docker, JWT, REST APIs, Carbon Interface API.}
      \resumeItemListEnd

    \resumeSubheading
      {Zidio Development}{Jun 2025 -- Sep 2025}
      {Java Full Stack}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Built a scalable microservices ecosystem using Spring Boot and Spring Cloud, setting up 16+ distinct services (including Recruitment, Analytics, and Payment) via Eureka Server for dynamic service discovery and centralized configuration management.}
        \resumeItem{Developed a secure API Gateway with JWT-based stateless authentication and load balancing, and created recruitment workflows featuring an asynchronous Email Service for real-time notifications and a File Upload Service with path sanitization for secure resume storage.}
        \resumeItem{Java, React.js, Tailwind CSS, Spring Boot, Spring Cloud, MySQL, API Gateway, Eureka, JWT, Microservices, REST APIs, Docker.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Carbon Personal Footprint App} $|$ \emph{Java, Spring Boot, React.js, MySQL, Tailwind CSS}}{2026}
          \resumeItemListStart
            \resumeItem{Built a full-stack sustainability dashboard using Spring Boot and React.js, integrating REST APIs for real-time carbon emission tracking and data visualization.}
            \resumeItem{Implemented a secure JWT authentication module using Spring Security and a gamified leaderboard system with efficient data persistence in MySQL.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{CRM Application} $|$ \emph{Java, Spring Boot, React.js, Microservices, Kafka}}{2025}
          \resumeItemListStart
            \resumeItem{Developed a comprehensive enterprise resource planning dashboard using Spring Boot microservices and React.js, integrating dynamic Kanban boards and real-time sales pipeline tracking.}
            \resumeItem{Configured a secure Role-Based Access Control (RBAC) system and an automated rule-processing workflow engine, utilizing Kafka for instant user notifications.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------CERTIFICATIONS---------------
\section{Certifications}
  \resumeItemListStart
    \resumeItem{\textbf{OCI Certified Developer Professional – Oracle (2025)}: Demonstrated proficiency in developing, testing, and securing high-performance cloud-native applications on Oracle Cloud Infrastructure.}
    \resumeItem{\textbf{OCI Certified AI Foundations Associate – Oracle (2025)}: Validated knowledge in foundational AI concepts including Machine Learning, Deep Learning, and Neural Networks across cloud platforms.}
    \resumeItem{\textbf{Data Structures and Performance – UC San Diego (2025)}: Mastered advanced Object-Oriented Programming principles, algorithmic performance tuning, and comprehensive unit testing in Java.}
  \resumeItemListEnd

\end{document}
